### 2014-11-02 thesis/results/results.tex
Finish results chapter

>>>>

In both the trauma and general hospital data sets, we were not able to
consistently improve the accuracy and AUC of all
classifiers with feature selection but we were able to sacrifice some
predictive power in order to use a drastically reduced feature set: for trauma
we found that K* with 11 features selected by a C4.5 wrapper performed only
slightly worse in discriminating between the two LOS classes than logistic
regression using 29 features, and for the hospital-wide data we achieved
0.983 AUC using only 2 features out of 14 using the MLP, 0.011 less than the
best result from logistic regression which required all 14 features. It is
therefore important to consider the trade-off between predictive ability,
speed and ease of understanding when making judgements about classifiers.

Finally, we pointed out that although discretisation was able to improve
classifier performance, this effect was less noticeable when more features
were discarded from feature selection. Discretisation has not been used
extensively in the LOS prediction literature, so our work will serve as a
starting point for further investigation.
